---
title: "Lab 00 - Hello IDS!"
author: "Aidan"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Casper", "Wen", "Santiago", "Jin", "Emily"),
  github_username = c("auxir", "NovaIMario", "SantiagosGitHub", 
                      "King-141319", "python151"), 
  colour = c("Blue", "Blue", "Red", 
             "Blue", "purple"),
  hobby = c("Gaming", "Gaming", "Football", 
            "Basketball", "Reading"),
  favourite_number = c(17, 7, 12, 19, pi)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Favourite number of each member of the group plotted against their GitHub username in their favourite colour

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite number",
          title = "Introductery graph")
```



### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A pie chart would probably be a better representation of this data as its size does not increase as new favourite hobbies are added
